---
title: "Project Milestone 4"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)
```


PENDING TASK FOR MS 4:
- Correct denominator for calculations
- Add any additional calculations aka corrections
- Rerun graph to update it 
- Add interpretation


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
ca_vax_county <- read_csv("ca_vax_county.csv")
CA_flu_merge_demo_2 <- read_csv("CA_flu_merge_demo_2.csv")
ca_vax_county_2 <- read_csv("ca_vax_county_2.csv")
CA_flu_merge <- read_csv("CA_flu_merge.csv")
CA_flu_merge_demo <- read_csv("CA_flu_merge_demo.csv")
```


Final datasets for creation of visualization
```{r}
CA_flu_vax <- merge(x = CA_flu_merge_demo, y = ca_vax_county, by = c("county", "quarter"), all = TRUE)
```

Additional calculations
```{r}
ca_vax_county_2 <- ca_vax_county_2 %>% 
  add_column(percent_partial_vax = ca_vax_county_2$total_partial_vax/ca_vax_county$susceptible *100) %>% 
  add_column(percent_atleast_one_dose = ca_vax_county_2$cum_atleast_one_dose/ca_vax_county$susceptible *100)
```

Visualization 1 - Comparing vax status among individuals within dataset
```{r}
library(tidyverse)

ca_vax_county_2 %>%
  gather(key, percent_fully_vax ,-quarter, -susceptible, -county, -cum_fully_vax, -cum_atleast_one_dose, -total_partial_vax, -cum_unvax) %>%
  ggplot(aes(x=quarter, y= percent_fully_vax, fill=key)) +
    geom_col(position = "dodge") +
  labs(x = "Quarter", y = "Percentage", fill = "Vaccine Status", title = "Vaccination Status in California by Quarter from September 2022 - June 2023") +
  scale_fill_discrete(labels = c("atleast one dose", "fully vaccinated", "partially vaccinated", "unvaccinated"))

```

Visualization 1 interpretation
```{r}

```

Visualization 2
```{r}

CA_flu_merge_demo_2 %>%
  gather(key, flu_incidence ,-quarter, -age_category, -county, -cumulative_severe, -current_infected, -new_infected, -new_severe, -susceptible) %>%
  ggplot(aes(x=quarter, y= flu_incidence, fill=key)) +
    geom_col(position = "dodge") +
  labs(x = "Quarter", y = "Percentage", fill = "Flu Cases", title = "Flu Incidence Cases in California by Quarter from September 2022 - June 2023") +
  scale_fill_discrete(labels = c("new infections", "severe infections")) 
  
```

Visualization 2 interpretation
```{r}

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
