---
title: "Project Milestone 6"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---
Authors: Kathy Nazarian, Kimberly Michel

```{r, include=FALSE}

library(readr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)
ca_vax_county <- read_csv("ca_vax_county.csv")
CA_flu_merge_demo_2 <- read_csv("CA_flu_merge_demo_2.csv")

CA_flu_vax <- merge(x = CA_flu_merge_demo_2, y = ca_vax_county, by = c("county", "quarter", "age_category"))

ca_vax_by_quarter <- ca_vax_county %>% 
  group_by(county, quarter) %>%
  summarise(susceptible = sum(susceptible),
            cum_fully_vax = sum(cum_fully_vax))

ca_vax_by_quarter <- ca_vax_by_quarter %>% 
  add_column(percent_fully_vax = ca_vax_by_quarter$cum_fully_vax/ca_vax_by_quarter$susceptible *100)
```

## Visualizations

```{r, echo = FALSE, message=FALSE}
chart_1_data <- ca_vax_by_quarter %>% 
  group_by(county) %>% 
  summarise(mean(percent_fully_vax)) %>% 
   rename(percent_fully_vax = "mean(percent_fully_vax)")


ggplot(chart_1_data, aes(x= reorder(county, -percent_fully_vax), y=percent_fully_vax)) +
    geom_bar(stat = "identity") +
  labs(x = "Counties in California", y = "% Vaccinated" ,
   title = "Fig.1: Percent of People Fully Vaccinated in each County in California", 
   subtitle = "From September 2022 to June 2023") +
  theme(axis.text.x = element_text(size = 9, angle = 45))

```

```{r, echo = FALSE, message= FALSE}
chart_2_data <- CA_flu_vax %>% 
 select(-susceptible.x, -susceptible.y, -new_infected, -current_infected, -new_severe, 
        -cumulative_severe, -cum_fully_vax, -cum_atleast_one_dose, -cum_unvax, -severe_incidence,
        -total_partial_vax) %>% 
  group_by(county, quarter) %>% 
  summarise(mean(flu_incidence)) %>%
  rename(flu_incidence = "mean(flu_incidence)")%>%
  pivot_wider(names_from = "quarter", 
              values_from = flu_incidence)

print(chart_2_data)
```

```{r, echo=FALSE}
CA_flu_merge_demo_2 %>%
  gather(key, flu_incidence ,-quarter,-age_category, -county, -cumulative_severe, -current_infected, -new_infected, -new_severe, -susceptible) %>%
  ggplot(aes(x=quarter, y= flu_incidence, fill=age_category)) +
    geom_col(position = "dodge") +
  labs(x = "Quarter", y = "Incidence Rate", fill = "Age Category", 
       title = "Fig. 2: Flu Incidence Cases in California by Quarter for each Age Category", 
       subtitle = "From September 2022 - June 2023") +
  scale_fill_discrete(labels = c("0-17", "18-49", "50-64", "65+"))
```

## Problem Statement

We wanted to identify whether there were any discrepancies or
disparities among flu infections in California between September 2022 -
June 2023. Comparing flu infections rates and vaccination rates by age
allowed us the opportunity to identify these gaps. Showcasing the data
by different age categories allows us to understand which groups are
affected most by severe or new infections based on vaccination rates.
This could allow us to further our research in implementing different
policies to close the gaps.

## Methods

Source: Datasets appear to be from health departments within CA and Los
Angeles. The data that was collected includes cases of flu as well as
vaccine uptake data. Timeframe of each dataset ranges between September
2022 - June 2023 within different counties across California.

Description of cleaning and creating new variables:

-   We renamed all data set column names to be in snake case and have
    similar names to each other to facilitate merging the data sets
    later.

-   New columns with formulas were created to calculate COVID
    vaccination rates and flu incidence rates for the respective data
    frame. In order to achieve this, we had to reformat several values
    from chr to num.

-   We cleaned data by removing columns in each data frame that we no
    longer needed. This included removing demographics that we did not
    use for analysis, including race/ethnicity and gender. We also
    excluded columns that would not be used for calculations, like the
    number of people who were unvaccinated or the number of new severe
    flu infections.

-   We created new datasets by merging several together. Los Angeles was
    initially excluded from the data set that included all other
    counties in California, so we were able to add it to that data set
    by making Los Angeles its own column. We then merged the COVID
    vaccination data set and the flu incidence data set to be able to
    analyze the relationship using one data frame.

-   The date category was adjusted to be by quarter. Quarters (Q1-4)
    were split up into 4 increments based on timeline in raw data. For
    reference:

    -   Q1 = Sep - Nov '22

    -   Q2 = Dec '22 - Feb '23

    -   Q3 = March - May '23

    -   Q4 = June '23

Analytic methods: Retrospective data analysis to identify vaccination and flu incidence rates among California residents among September 2022 - June 2023.

## Results + Discussion

Figure 1 demonstrates the average COVID-19 vaccination rates of all counties in California, only including those that are fully vaccinated. The graph shows that Imperial County (94.6%) and Lassen County (33.7%) have the highest and lowest vaccination rates among all counties. Figure 2 display that Quarter 2 (Dec '22 - Feb '23), had the highest flu incidence rates among all age groups, following Q3 (March - May '23), and Q1 (Sep - Nov '22), respectively. Q4 (June '23) had no data. 

Based on the results of our graphs, we can conclude that there was no correlation between COVID-19 vaccination rates and flu incidence rates in California between September 2022 - June 2023. Although there is a notable difference in vaccination rates within the counties, the average incidence rates for each quarter are similar for each county, further solidifying that there is no correlation between the two. The pattern in Figure 2 tells us that the highest flu incidence rates occurred during Quarter 2, between December 2022 and February 2023. This could be due to several external factors such as flu season during the colder seasons as there was no difference in COVID vaccination rates during this time. 
