---
title: "Project Milestone 3"
output: html_notebook
---

Authors: Katherine Nazarian, Kimberly Michel

```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)

CA_flu <- read_csv("CA_flu.csv")
View(CA_flu)
LACounty_flu <- read_csv("LACounty_flu.csv")
View(LACounty_flu)
ca_vax <- read_csv("ca_vax.csv")
View(ca_vax)

```

## Subset rows or columns, as needed
```{r}
LACounty_flu <- LACounty_flu %>% 
  add_column(county = "LA County")

LACounty_1 <- LACounty_flu %>% 
  rename("current_infected" = infected_current, 
         "new_recovered" = recovered_new, 
         "new_infected" = dx_new, 
         "cumulative_infected" = infected_cum, 
         "cumulative_recovered" = recovered_cum, 
         "new_severe" = severe_new, 
         "cumulative_severe" = severe_cum) %>% 
  select(-race_eth, -dt_report) %>% 
   mutate(county = word(county , 1  , -2)) %>% 
  mutate(
    quarter = case_when(
      date >= "2022-09-24" & date <= "2022-11-30" ~ 'Q1', 
      date >= "2022-12-01" & date <= "2023-02-28" ~ 'Q2', 
      date >= "2023-03-01" & date <= "2023-05-31" ~ 'Q3', 
      date >= "2023-06-01" ~ 'Q4'))


CA_flu1 <- CA_flu %>% 
  rename("susceptible" = count_susceptible, 
         "new_infected" = new_infections, 
         "age_category" = age_cat, 
         "date" = dt_diagnosis) %>% 
  select(-time_int, -race_ethnicity, -report_date, -pop, 
         -new_unrecovered, -cumulative_unrecovered) %>%
  mutate(county = word(county , 1  , -2)) %>%
  mutate(
    quarter = case_when(
      date >= "2022-09-24" & date <= "2022-11-30" ~ 'Q1', 
      date >= "2022-12-01" & date <= "2023-02-28" ~ 'Q2', 
      date >= "2023-03-01" & date <= "2023-05-31" ~ 'Q3', 
      date >= "2023-06-01" ~ 'Q4'))


```



```{r}

```

## Clean variables needed for analysis (minimum 2)

Examples Recode invalid values, Handle missing data, Recode categories

```{r}

ca_vax1 <- ca_vax %>% 
  rename("county" = county_name, "susceptible" = est_population, "age_category" = demographic_value) %>%
  filter(demographic_category == "Age Group") %>% 
  select(-county_type, -suppress_data) %>% 
  na.omit()
```

## Data re-structured as needed
(aggregated/summarized and/or pivoted)

## Create new variables needed for analysis (minimum 2)
New variables should be created based on existing columns; for example Calculating a rate, Combining character strings, Aggregation

```{r}

CA_flu_merge <- merge(x = CA_flu1, y = LACounty_1, by = c("county", "age_category", "quarter", "sex", "new_infected", "new_recovered", "susceptible", "current_infected", "cumulative_infected", "cumulative_recovered", "new_severe", "cumulative_severe"), all = TRUE)

CA_flu_merge_demo <- CA_flu_merge %>% 
  group_by(county, age_category, quarter) %>% 
  summarize(susceptible = sum(susceptible),
            new_infected = sum(new_infected), 
            current_infected = sum(current_infected), 
            new_severe = sum(new_severe), 
            cumulative_severe = sum(cumulative_severe))

CA_flu_merge_age <- CA_flu_merge %>% 
  group_by(age_category) %>% 
  summarize(susceptible = sum(susceptible),
            new_infected = sum(new_infected), 
            current_infected = sum(current_infected), 
            new_severe = sum(new_severe), 
            cumulative_severe = sum(cumulative_severe))

ca_vax2 <- ca_vax1 %>% 
  mutate(
    quarter = case_when(
      quarter >= "2022-09-24" & quarter <= "2022-11-30" ~ 'Q1', 
      quarter >= "2022-12-01" & quarter <= "2023-02-28" ~ 'Q2', 
      quarter >= "2023-03-01" & quarter <= "2023-05-31" ~ 'Q3', 
      quarter >= "2023-06-01" ~ 'Q4')) %>% 
  na.omit()

ca_vax_county <- ca_vax2 %>% 
  group_by(county, quarter, age_category) %>% 
  select(-demographic_category) %>% 
  summarize(susceptible = sum(susceptible), 
            cum_fully_vax = sum(cum_fully_vax), 
            total_partial_vax = sum(total_partial_vax),
            cum_atleast_one_dose = sum(cum_atleast_one_dose),
            cum_unvax = sum(cum_unvax)) %>%
  mutate(
    age_category = case_when(
      age_category == "Under 5" | age_category == "5-11" | age_category == "12-17" ~ "0-17",
      age_category == "18-49" ~ "18-49",
      age_category == "50-64" ~ "50-64", 
      age_category == "65+" ~ "65+")) %>% 
  group_by(county, quarter, age_category) %>% 
  summarise_all(sum)

ca_vax_by_quarter <- ca_vax_county %>% 
  group_by(county, quarter) %>%
  summarise(susceptible = sum(susceptible),
            cum_fully_vax = sum(cum_fully_vax)) %>% 
  add_column(percent_fully_vax = edit_ca_vax_by_Q$cum_fully_vax/edit_ca_vax_by_Q$susceptible *100)

 

CA_flu_merge_demo_2 <- CA_flu_merge_demo %>% 
  add_column(flu_incidence = CA_flu_merge_demo$new_infected/CA_flu_merge_demo$susceptible *100) %>% 
  add_column(severe_incidence = CA_flu_merge_demo$new_severe/CA_flu_merge_demo$susceptible *100)
  

CA_flu_vax <- merge(x = CA_flu_merge_demo_2, y = ca_vax_county, by = c("county", "quarter", "age_category"))

```

## One or more tables with descriptive statistics for 4 data elements

```{r}
head(CA_flu_merge_demo_2)
```


```{r}

```

## Data dictionary based on clean dataset (minimum 4 data elements), including:

Variable name, Data type, Description


1. (CA_flu_merge_demo_2): Formulas
    flu_incidence = new infected/susceptible *100
    severe_incidence = new severe/susceptible *100

2. Susceptible = n of population 

3. (CA_flu_merge_demo_2) - Quarter (Q1-4) split up into 4 increments based on timeline in raw data. Q1 = Sep - Nov ’22, Q2 = Dec ’22 - Feb ’23, Q3 = March - May ’23, Q4 = June ‘24

4. (CA_vax_county_2): Definitions
  cum_fully_vax = n of individuals that have received entire series of vax +            booster if needed
  total_partial_vax = n of individuals who have received entire series of vax but       have not received booster
  cum_atleast_one_dose = n of individuals who have received at least one dose with no booster 




```{r}
readr::write_csv(CA_flu_merge, "CA_flu_merge.csv")
readr::write_csv(CA_flu_merge_demo, "CA_flu_merge_demo.csv")
readr::write_csv(ca_vax_county, "ca_vax_county.csv")
readr::write_csv(CA_flu_merge_demo_2, "CA_flu_merge_demo_2.csv")
readr::write_csv(ca_vax_county_2, "ca_vax_county_2.csv")

```

```

## Html output that is professionally prepared for presentation

Only the necessary information is outputted (you should suppress, for example, entire data frame outputs) Use of headers and sub headers to create an organized document

```{r}
ggplot(data = nyc_df, aes(x= reorder(boroughs_nyc, +bll_over_5), y=bll_over_5)) +
  geom_bar(stat = 'identity',color='#003886',fill='#ff6600')+
  labs(x="boroughs", y="counts of BLL >5ug/dL",
  title ="New York City: Elevated Blood Lead Levels 2005-2016 by Borough") +
  theme_bw()
```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

