---
title: "Project Milestone 2"
output:
  pdf_document: default
  html_notebook: default
---
Authors: Kathy Nazarian, Kimberly Michel


```{r}
#packages needed
library(readr)
library(lubridate)
library(dplyr)
library(tidyverse)
```

```{r}

```
\newpage 
### Import Data Sets
```{r}
ca_vax_rates_quarter <- read_csv("ca_vax_rates_quarter.csv")
ca_vax <- ca_vax_rates_quarter

sim_flu_CA <- read_csv("sim_flu_CA.csv")
CA_flu <- sim_flu_CA

sim_flu_LACounty <- read_csv("sim_flu_LACounty.csv")
LACounty_flu <- sim_flu_LACounty
```
\newpage 

### Clean Data using Snake Case
```{r}
names(ca_vax)[1] <- 'county_name'
names(ca_vax)[2] <- 'county_type'
names(ca_vax)[3] <- 'demographic_category'
names(ca_vax)[4] <- 'demographic_value'
names(ca_vax)[5] <- 'est_population'
names(ca_vax)[6] <- 'date_admin'
names(ca_vax)[7] <- 'total_partial_vax'
names(ca_vax)[8] <- 'cum_fully_vax'
names(ca_vax)[9] <- 'cum_atleast_one_dose'
names(ca_vax)[10] <- 'cum_unvax'
names(ca_vax)[11] <- 'suppress_data'
names(ca_vax)[12] <- 'cum_up_to_date_vax'
names(ca_vax)[13] <- 'quarter'

names(LACounty_flu)[1] <- 'date'
names(LACounty_flu)[2] <- 'age_category'
names(LACounty_flu)[3] <- 'sex'
names(LACounty_flu)[4] <- 'race_eth'
names(LACounty_flu)[5] <- 'dt_report'
names(LACounty_flu)[6] <- 'dx_new'
names(LACounty_flu)[7] <- 'recovered_new'
names(LACounty_flu)[8] <- 'infected_current'
names(LACounty_flu)[9] <- 'infected_cum'
names(LACounty_flu)[10] <- 'recovered_cum'
names(LACounty_flu)[11] <- 'susceptible'
names(LACounty_flu)[12] <- 'severe_new'
names(LACounty_flu)[13] <- 'severe_cum'

```
\newpage

### Data Cleaning for LACounty_flu ds

```{r}
#dt_dx string is 'chr', must be changed to date

str(LACounty_flu)

#reformat date in LACounty_flu dataset from chr to date format
LACounty_flu <- LACounty_flu %>%
  mutate(date = as.Date(as.character(LACounty_flu$date), format = "%d%b%Y"))

#data cleaned by descending order by dt_dx
LACounty_flu <- LACounty_flu[order(LACounty_flu$date),]
```

### Data Cleaning for CA_flu ds

```{r}
# data cleaning for CA_flu ds
#data cleaned by descending order of diagnosis date
CA_flu <- CA_flu[order(CA_flu$dt_diagnosis),]

```
### Data Cleaning for ca_vax ds

```{r}
#data cleaning for ca_vax ds

#data reorganized by descending order of date vax was given
ca_vax <- ca_vax[order(ca_vax$date_admin),]
```
\newpage

### Structure of each df:

```{r}
str(CA_flu)
```


```{r}
str(LACounty_flu)
```


```{r}
str(ca_vax)
```

### Data Type Descriptions

```{r}
summary(ca_vax_rates_quarter$`Estimated Population`)
```


```{r}
summary(ca_vax_rates_quarter$`Estimated Population`)
```


```{r}
summary(ca_vax_rates_quarter$`Cumulative Fully Vaccinated`)
```


```{r}
summary(ca_vax_rates_quarter$`Cumulative Unvaccinated`)
```


```{r}
summary(sim_flu_CA$new_infections)
```


```{r}
summary(sim_flu_CA$new_severe)
```
\newpage

### Description of dataset:

Datasets appear like they were collected by a health department within CA or Los Angeles. The data that was collected includes cases of flu as well as vaccine uptake data. Timeframe of each dataset ranges between 2020-2023 within different counties across California.

Question/Statement: Reporting whether there’s any correlation between flu vaccination rates and covid vaccination rates.

The dataset provides vaccination rates within many counties in california as well as the amount of cases. This will allow us to conduct our analysis in order to determine whether there’s any correlation between flu and covid vaccination rates by running appropriate statistical tests.

### 5+ data types:

-Population sizes 
This information is essential as it’ll allow us to conduct our calculations in order to determine rates.

-Cumulative up to date vaccinated/unvaccinated (exposure)
Will be using this data to calculate vaccination rates in order to compare them to flu rates among exposed and unexposed

-New severe
Will be using this data (incidence rate) to compare to exposed and unexposed populations (vaccinated/unvaccinated)

-County
Could be a confounding variable. Could assess whether some counties have higher vaccination/flu rates which would be considered a disparity.

-Age 
Could be a counting variable as well. We could use direct standardization in order to see the crude rates among different age groups in order to assess whether certain age groups have higher rates than others.

### Data cleaning:

Completed:
 -renamed all dataset column names by snake case
 -Changed LACounty flu “dt_dx” column from chr string to date, then arranges in chronological order + removed extra columns + moved “date” column to first

Need to be cleaned:
 -Demographic value needs to be reformatted from chr to num (ca_vax)
 -age needs to be reformatted from chr to num (LACounty_flu)
 -Age_cat needs to be reformatted from chr to number (ca_flu)
 -Ethnicity needs to be reformatted from num to chr (ca_flu)


```{r}
readr::write_csv(CA_flu, "CA_flu.csv")
readr::write_csv(LACounty_flu, "LACounty_flu.csv")
readr::write_csv(ca_vax, "ca_vax.csv")
```

