---
title: "Project Milestone 6"
output:
  html_document:
    df_print: paged
---

```{r, include=FALSE}

library(readr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)
ca_vax_county <- read_csv("ca_vax_county.csv")
CA_flu_merge_demo_2 <- read_csv("CA_flu_merge_demo_2.csv")

CA_flu_vax <- merge(x = CA_flu_merge_demo_2, y = ca_vax_county, by = c("county", "quarter", "age_category"))

ca_vax_by_quarter <- ca_vax_county %>% 
  group_by(county, quarter) %>%
  summarise(susceptible = sum(susceptible),
            cum_fully_vax = sum(cum_fully_vax))

ca_vax_by_quarter <- ca_vax_by_quarter %>% 
  add_column(percent_fully_vax = ca_vax_by_quarter$cum_fully_vax/ca_vax_by_quarter$susceptible *100)
```

Visualizations (at least one per team member)
One print quality table as requested in scenario
One print quality plot or chart as requested in scenario
For groups of 3, one additional print quality table or plot of your choice (can support the requested data in the scenario, or answer a different question using the same data sources)


```{r, echo = FALSE, message=FALSE}
chart_1_data <- ca_vax_by_quarter %>% 
  group_by(county) %>% 
  summarise(mean(percent_fully_vax)) %>% 
   rename(percent_fully_vax = "mean(percent_fully_vax)")


ggplot(chart_1_data, aes(x= reorder(county, -percent_fully_vax), y=percent_fully_vax)) +
    geom_bar(stat = "identity") +
  labs(x = "Counties in California", y = "% Vaccinated" ,
   title = "Percent of People Fully Vaccinated in each County in California", 
   subtitle = "From September 2022 to June 2023") +
  theme(axis.text.x = element_text(size = 9, angle = 45))

```

```{r, echo = FALSE, message= FALSE}
chart_2_data <- CA_flu_vax %>% 
 select(-susceptible.x, -susceptible.y, -new_infected, -current_infected, -new_severe, 
        -cumulative_severe, -cum_fully_vax, -cum_atleast_one_dose, -cum_unvax, -severe_incidence,
        -total_partial_vax) %>% 
  group_by(county, quarter) %>% 
  summarise(mean(flu_incidence)) %>%
  rename(flu_incidence = "mean(flu_incidence)")%>%
  pivot_wider(names_from = "quarter", 
              values_from = flu_incidence)

print(chart_2_data)
```
```{r, echo=FALSE}
CA_flu_merge_demo_2 %>%
  gather(key, flu_incidence ,-quarter,-age_category, -county, -cumulative_severe, -current_infected, -new_infected, -new_severe, -susceptible) %>%
  ggplot(aes(x=quarter, y= flu_incidence, fill=age_category)) +
    geom_col(position = "dodge") +
  labs(x = "Quarter", y = "Incidence Rate", fill = "Age Category", 
       title = "Flu Incidence Cases in California by Quarter for each Age Category", 
       subtitle = "From September 2022 - June 2023") +
  scale_fill_discrete(labels = c("0-17", "18-49", "50-64", "65+"))
```

Problem Statement (1-2 paragraphs)
```{r}

```

Methods, for each data source
  Source
  Years and/or dates of data
  Description of cleaning and creating new variables
  Analytic methods
```{r}

```

Results
```{r}

```

Discussion (interpretation of results)
Maximum of 1,000 words

