---
title: "Project Milestone 3"
output: html_notebook
---

Authors: Katherine Nazarian, Kimberly Michel

## Subset rows or columns, as needed

```{r}
plot(cars)
```

## Create new variables needed for analysis (minimum 2)

New variables should be created based on existing columns; for example Calculating a rate Combining character strings Aggregation

```{r}

```

## Clean variables needed for analysis (minimum 2)

Examples Recode invalid values Handle missing data Recode categories

```{r}

```

## Data re-structured as needed

(aggregated/summarized and/or pivoted)

```{r}

```

## Data dictionary based on clean dataset (minimum 4 data elements), including:

Variable name Data type Description

```{r}

```

## One or more tables with descriptive statistics for 4 data elements

```{r}

```

## Html output that is professionally prepared for presentation

Only the necessary information is outputted (you should suppress, for example, entire data frame outputs) Use of headers and sub headers to create an organized document

```{r}

```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}

```
