---
title: "Project Milestone 4"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)
```

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
ca_vax_county <- read_csv("ca_vax_county.csv")
CA_flu_merge_demo_2 <- read_csv("CA_flu_merge_demo_2.csv")
ca_vax_county_2 <- read_csv("ca_vax_county_2.csv")
CA_flu_merge <- read_csv("CA_flu_merge.csv")
CA_flu_merge_demo <- read_csv("CA_flu_merge_demo.csv")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
